---
title: "Allen Institute Brain Data"
author:
- name: Dario Righelli
  affiliation: Department of Statistical Sciences, University of Padova
  email: dario.righelli@gmail.com
package: AllenInstituteBrainData
output:
    BiocStyle::html_document
abstract: |
    This package retrieves data from Allen Brain Institute NEMO repository and
    shape them in a Bioconductor data structure form for further use, such as
    data investigation and analysis or as cell annotation reference.
vignette: |
    %\VignetteIndexEntry{Allen Institute Brain Data}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

# Description

This package retrieves data from Allen Brain Institute NEMO repository and shape
them in a Bioconductor data structure form for further use, such as data 
investigation and analysis or as cell annotation reference.

# Available Datasets

A list of available datasets and associated `DataType`:

+ `Allen_Mouse_2020` : retrieves the Zeng dataset of 31053 features and 1169213 
cells for mouse brain data related to year 2020. (ref to be specified)


# Retrieving Data

To retrieve data simply use the `AllenInstituteBrainData` function, it queries
the NeMO Allen Institute database for the specified `DataType` argument.
The function returns a `SingleCellExperiment` data object.

```{r}
library(AllenInstituteBrainData)
(sce <- AllenInstituteBrainData("Allen_Mouse_2020"))
```




# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
